Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-01 analysis/paper/paper.Rmd
Apply Bec's suggestion for model description paragraph for clarity

The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
To predict the responses with publishing journal, as the journals' abbreviation, the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

>>>>

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 to predict two responses with publishing journal, as the journals’ abbreviation, the formula took the form: response ~ abbreviation (model 1: code_availability ~ abbreviation and model 2: data_availability ~ abbreviation) and the models included assignee as a random effect (formula: ~1 | assignee).
Models 3 and 4 to predict the two responses with year (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). 
Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
